The importance of transient resonances in extreme-mass-ratio inspirals

### 2016-08-15 res_char.tex
RevTeX 4.1

\documentclass[aps,prd,amsfonts,amssymb,amsmath,nofootinbib,showpacs,superscriptaddress,twocolumn]{revtex4}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{psfrag}
\usepackage{mathrsfs}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{textcomp}

@@

A given EMRI is classified as observable if its SNR exceeds some threshold value $\rho\sub{thres}$. Calculating SNRs from the generated AK waveforms, assuming $6$ laser links and using the eLISA PSD\cite{Amaro-Seoane2012a}, we find $513$ detectable events across the mission for $\rho\sub{thres} = 15$ (cf.\ \cite{Gair2004,Amaro-Seoane2012a,Mapelli2012}). The parameter distributions for the mass and spin of the SMBH, the orbital shape parameters at plunge, the redshift of the source, and the length of the observation $t\sub{insp}$ are shown in \figref{EMRIpar-dists}, to be contrasted with the distributions of the $5820$ systems with an SNR less than $15$, which are also shown.

>>>>

\documentclass[aps,prd,amsfonts,amssymb,amsmath,nofootinbib,showpacs,superscriptaddress,twocolumn,floatfix]{revtex4-1}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{psfrag}
\usepackage{mathrsfs}
\usepackage{dcolumn}
\usepackage[breaklinks=true]{hyperref}
\usepackage{textcomp}

@@

A given EMRI is classified as observable if its SNR exceeds some threshold value $\rho\sub{thres}$. Calculating SNRs from the generated AK waveforms, assuming $6$ laser links and using the eLISA PSD~\cite{Amaro-Seoane2012a}, we find $513$ detectable events across the mission for $\rho\sub{thres} = 15$ (cf.\ \cite{Gair2004,Amaro-Seoane2012a,Mapelli2012}). The parameter distributions for the mass and spin of the SMBH, the orbital shape parameters at plunge, the redshift of the source, and the length of the observation $t\sub{insp}$ are shown in \figref{EMRIpar-dists}, to be contrasted with the distributions of the $5820$ systems with an SNR less than $15$, which are also shown.
